### 2021-06-26 phd/thesis plan/MainText/chapter1.tex
added a SwAV dataset preparer

\section{Literature Review}\label{literature-review}
\subsection{Signs Language Recognition and annotation}
Signs Language Recognition (SLR) are roughly divided in two categories Isolated SLR and Continuous SLR\cite{adaloglou2020comprehensive} figure \ref{fig-slr} shows tasks involved on SLR.

>>>>

\section{Literature Review}\label{literature-review}
\subsection{Self Supervised Learning}
Predicting the future or reconstructing the past is a way to learn and understanding the hidden patterns and distributions in data which is not necessarily annotated or pre-processed. Schmidhuber proposed an early self supervised method \cite{schmidhuber1990making} where two fully self supervised recurrent neural networks predicted future reinforcement based on external interactions and state sent to the next network cell is calculated on differences on successive predictions achieving a system capable to generate supervision signals. Unlike supervised tasks where predictions are influenced by target and observed variables, self supervised tasks are influenced in a greater extent by hidden or invisible variables also known as latent variables

\subsubsection{Pretext Tasks}
\subsubsection{Self Supervised Representation Learning}
\subsection{Signs Language Recognition and annotation}
Signs Language Recognition (SLR) are roughly divided in two categories Isolated SLR and Continuous SLR\cite{adaloglou2020comprehensive} figure \ref{fig-slr} shows tasks involved on SLR.
